---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pathfinder

[![Travis build status](https://travis-ci.org/dSHARP-CMU/pathfinder.svg?branch=master)](https://travis-ci.org/dSHARP-CMU/pathfinder)
[![Coverage status](https://codecov.io/gh/dSHARP-CMU/pathfinder/branch/master/graph/badge.svg)](https://codecov.io/github/dSHARP-CMU/pathfinder?branch=master)
  
The goal of pathfinder is to find a path across multiple edge bundles in a graph that minimizes the nubmer of times each bundle is traversed.

## Installation

You can install the development version:

```{r, eval = FALSE}
devtools::install_github("dSHARP-CMU/pathfinder")
```

## Usage

Starting with an igraph object, specify edge bundles that must be traversed by using a list of edge indices:

```{r}
# A small subset of road data from Pittsburgh
pgh_graph

pgh_distances

# Edges belonging to Pittsburgh bridges
pgh_bundles
```

`greedy_search()` will traverse teh graph by jumping from closest edge bundle to closest edge bundle.
By setting `penalize = TRUE` you can add a sever edge weight penalty to crossed bundles to disincentivize crossing bundles more than once.

```{r}
unpenalized_run <- greedy_search(graph, edge_bundles = bundles, distances = edge_distances)

```

```{r}
