---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "svg"
)

options("max.print" = 20)
```

# pathfinder

[![Travis build status](https://travis-ci.org/cmu-lib/pathfinder.svg?branch=master)](https://travis-ci.org/cmu-lib/pathfinder)
[![Coverage status](https://codecov.io/gh/cmu-lib/pathfinder/branch/master/graph/badge.svg)](https://codecov.io/github/cmu-lib/pathfinder?branch=master)

pathfinder provides functions for complex pathfinding within a graph and topology simplification functions.

## Installation

You can install the development version:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("cmu-lib/pathfinder")
```

## Context

This package is one of several originally developed by [Matthew Lincoln](https://github.com/mdlincoln) for use by Carnegie Mellon University's ["Bridges of Pittsburgh"](http://bridgesofpittsburgh.net/) project:

- [konigsberger] (end-user package)
  - [pathfinder]
  - [bigosm]

[konigsberger]: https://cmu-lib.github.io/konigsbergr/index.html

[pathfinder]: https://github.com/cmu-lib/pathfinder/

[bigosm]: https://github.com/cmu-lib/bigosm

