---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "svg"
)

options("max.print" = 20)
```

# pathfinder

[![Travis build status](https://travis-ci.org/dSHARP-CMU/pathfinder.svg?branch=master)](https://travis-ci.org/dSHARP-CMU/pathfinder)
[![Coverage status](https://codecov.io/gh/dSHARP-CMU/pathfinder/branch/master/graph/badge.svg)](https://codecov.io/github/dSHARP-CMU/pathfinder?branch=master)
  
The goal of pathfinder is to find a path across multiple edge bundles in a graph that minimizes the number of times each bundle is traversed.

## Installation

You can install the development version:

```{r, eval = FALSE}
devtools::install_github("dSHARP-CMU/pathfinder")
```

## Usage

Starting with an igraph object, specify edge bundles that must be traversed by using a list of edge indices:

```{r, include = FALSE}
library(pathfinder)
```

```{r}
# A small subset of road data from Pittsburgh
pgh_graph

pgh_distances

# Edges belonging to Pittsburgh bridges
pgh_bundles
```

`greedy_search()` will traverse the graph by walking a path from the starting vertex to the nearest edge bundle, crossing that bundle, then finding the next closest bundle, until all bundles have been crossed at least once.
By setting `penalize = TRUE` you can add a severe edge weight penalty to crossed bundles to discourage crossing bundles more than once.

```{r}
penalized_run <- greedy_search(pgh_graph, 
                               edge_bundles = pgh_bundles, 
                               distances = pgh_distances, 
                               penalize = TRUE)
```

```{r, echo=FALSE, warning=FALSE}
suppressPackageStartupMessages({
  library(konigsbergr)
  library(sf)
})

render_pathway_plot <- function(graph, bundles, distances, pathway) {
  plot_graph <- decorate_graph(graph, bundles, distances)
  E(plot_graph)$edge_mark[unique_pathway_edges(pathway)] <- "path"
  E(plot_graph)$edge_mark[which(!is.na(E(plot_graph)$pathfinder.bundle_id))] <- "bundled"
  
  graph_sf <- edges_to_sf(plot_graph)
  penalized_augment <- augment(penalized_run)
  penalized_solution <- graph_sf[unique(penalized_augment$edge_id),]
  
  plot(st_geometry(graph_sf), col = "gray80", reset = FALSE)
  plot(penalized_solution["edge_mark"], pal = c(path = "blue", bundled = "red"), lwd = 2, add = TRUE)
}

render_pathway_plot(pgh_graph, pgh_bundles, pgh_distances, penalized_run)
```

It's also possible to supply penalty functions that will completely prohibit recrossing edge bundles, however this may result in incomplete paths that get trapped.

```{r}
infinite_run <- greedy_search(pgh_graph, 
                              edge_bundles = pgh_bundles, 
                              distances = pgh_distances, 
                              penalize = TRUE, 
                              penalty_fun = penalize_inf)
```

Tidying methods are also available to get summary statistics on resulting pathways at different levels of resolution. 

```{r}
augment(penalized_run)
```

For more info, see `?glance`, `?tidy`, `?augment`

## Context

This package is one of several originally developed by [Matthew Lincoln](https://github.com/mdlincoln) for use by Carnegie Mellon University's ["Bridges of Pittsburgh"](http://bridgesofpittsburgh.net/) project:

- [konigsberger] (end-user package)
  - [pathfinder]
  - [bigosm]
  - [simplygraph]

[konigsberger]: https://dsharp-cmu.github.io/konigsbergr/index.html

[pathfinder]: https://github.com/dSHARP-CMU/pathfinder/

[simplygraph]: https://github.com/dSHARP-CMU/simplygraph

[bigosm]: https://github.com/dSHARP-CMU/bigosm

