---
title: "Pathfinding"
output: rmarkdown::html_vignette
author: "Matthew Lincoln"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Pathfinding}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r library, include = FALSE}
library(pathfinder)
```

Starting with an igraph object, specify edge bundles that must be traversed by using a list of edge indices:

```{r data}
# A small subset of road data from Pittsburgh
pgh_graph

pgh_distances

# Edges belonging to Pittsburgh bridges
pgh_bundles
```

`greedy_search()` will traverse the graph by walking a path from the starting vertex to the nearest edge bundle, crossing that bundle, then finding the next closest bundle, until all bundles have been crossed at least once.
By setting `penalize = TRUE` you can add a severe edge weight penalty to crossed bundles to discourage crossing bundles more than once.

```{r penalized-run}
penalized_run <- greedy_search(pgh_graph, 
                               edge_bundles = pgh_bundles, 
                               distances = pgh_distances, 
                               penalize = TRUE)
```

```{r pathway-plot}
render_pathway_plot <- function(graph, bundles, distances, pathway) {
  plot_graph <- decorate_graph(graph, bundles, distances)
  
  # In this case we're looking at 
  plot_layout <- cbind(
    V(plot_graph)$lon,
    V(plot_graph)$lat
  )
  
  pathway_augmented <- augment_edges(pathway)
  
  plot(plot_graph, 
       layout = plot_layout,
       vertex.size = 0.1, 
       vertex.label = NA, 
       edge.label = NA, 
       curved = FALSE, 
       edge.arrow.mode = 0,
       edge.color = c(path = "blue", bundled = "red", none = "gray80")[pathway_augmented$edge_type],
       edge.width = c(path = 2, bundled = 3, none = 0.2)[pathway_augmented$edge_type])
}

render_pathway_plot(pgh_graph, pgh_bundles, pgh_distances, penalized_run)
```

It's also possible to supply penalty functions that will completely prohibit recrossing edge bundles, however this may result in incomplete paths that get trapped.

```{r stopped-pathway}
infinite_run <- greedy_search(pgh_graph, 
                              edge_bundles = pgh_bundles, 
                              distances = pgh_distances, 
                              penalize = TRUE, 
                              penalty_fun = penalize_inf)

render_pathway_plot(pgh_graph, pgh_bundles, pgh_distances, infinite_run)
```

Tidying methods are also available to get summary statistics on resulting pathways at different levels of resolution:

One line per pathway:

```{r glance}
glance_path(penalized_run)
```

One line per edge in the graph

```{r augment-edges}
augment_edges(penalized_run)
```

Or one line per edge crossed in the path (may)

```{r augment-path}
augment_path(penalized_run)
```
