---
title: "Pathfinding"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pathfinding}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
library(pathfinder)
```

Starting with an igraph object, specify edge bundles that must be traversed by using a list of edge indices:

```{r}
# A small subset of road data from Pittsburgh
pgh_graph

pgh_distances

# Edges belonging to Pittsburgh bridges
pgh_bundles
```

`greedy_search()` will traverse the graph by walking a path from the starting vertex to the nearest edge bundle, crossing that bundle, then finding the next closest bundle, until all bundles have been crossed at least once.
By setting `penalize = TRUE` you can add a severe edge weight penalty to crossed bundles to discourage crossing bundles more than once.

```{r}
penalized_run <- greedy_search(pgh_graph, 
                               edge_bundles = pgh_bundles, 
                               distances = pgh_distances, 
                               penalize = TRUE)
```

```{r, eval=FALSE, echo=FALSE, warning=FALSE}
suppressPackageStartupMessages({
  library(konigsbergr)
  library(sf)
})

render_pathway_plot <- function(graph, bundles, distances, pathway) {
  plot_graph <- decorate_graph(graph, bundles, distances)
  E(plot_graph)$edge_mark[unique_pathway_edges(pathway)] <- "path"
  E(plot_graph)$edge_mark[which(!is.na(E(plot_graph)$pathfinder.bundle_id))] <- "bundled"
  
  graph_sf <- edges_to_sf(plot_graph)
  penalized_augment <- augment(penalized_run)
  penalized_solution <- graph_sf[unique(penalized_augment$edge_id),]
  
  plot(st_geometry(graph_sf), col = "gray80", reset = FALSE)
  plot(penalized_solution["edge_mark"], pal = c(path = "blue", bundled = "red"), lwd = 2, add = TRUE)
}

render_pathway_plot(pgh_graph, pgh_bundles, pgh_distances, penalized_run)
```

It's also possible to supply penalty functions that will completely prohibit recrossing edge bundles, however this may result in incomplete paths that get trapped.

```{r}
infinite_run <- greedy_search(pgh_graph, 
                              edge_bundles = pgh_bundles, 
                              distances = pgh_distances, 
                              penalize = TRUE, 
                              penalty_fun = penalize_inf)
```

Tidying methods are also available to get summary statistics on resulting pathways at different levels of resolution. 

```{r}
augment(penalized_run)
```

For more info, see `?glance`, `?tidy`, `?augment`
