---
title: "Simplifying Graphs"
output: rmarkdown::html_vignette
author: "Matthew Lincoln"
vignette: >
  %\VignetteIndexEntry{simplifying-graphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Say you have a graph where multiple nodes could be removed while still maintaining the same intersections between paths:

```{r build, message=FALSE}
set.seed(100)
library(igraph)
library(pathfinder)

graph <- igraph::graph_from_edgelist(
  matrix(c(
    "a", "b",
    "b", "f",
    "b", "d",
    "d", "c",
    "d", "e",
    "e", "k",
    "j", "k",
    "f", "g",
    "c", "h",
    "h", "i",
    "f", "j"
  ), ncol = 2, byrow = TRUE),
  directed = FALSE
)

edge_attr(graph, "distance") <- sample(1:10, size = ecount(graph), replace = TRUE)

plot(graph, edge.label = edge_attr(graph, "distance"))
```

Nodes `j`, `k`, `e`, `c`, and `h` could be removed without fundamentally altering the relationship of path intersections in this graph. `simplify_topology()` finds those 2-degree nodes and removes them, rewiring the remaining tangent nodes. Edge attributes will be merged with functions passed by the user via `edge_attr_comb`.

```{r simplify, message=FALSE}
simple_graph <- simplify_topology(graph, edge_attr_comb = list(distance = sum))

plot(simple_graph, edge.label = edge_attr(simple_graph, "distance"))
```
